Test a simpler version of veb-boost performance on ukbiobank data

### 2020-05-20 analysis/simulation-simpleveb-boost-ukbchr22.Rmd
test mr.ash2

@@

MR.ASH results (start from gene):
```{r sim 1}
load(paste0(outputdir, "mr.ash2_20200503-1-mr.ash2.expr-res.Rd"))
g.fit <- mr.ash2.fit$fit1
s.fit <-  mr.ash2.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)
```

MR.ASH results (start from SNP):
```{r sim 1}
load(paste0(outputdir, "mr.ash2_20200503-1-mr.ash2.snp-res.Rd"))
g.fit <- mr.ash2.fit$fit2
s.fit <-  mr.ash2.fit$fit1
summary_mr.ash2(g.fit, s.fit, phenores)
```

@@

True parameters:
```{r para 2}
readLines(paste0(outputdir, "param-20200429-2.R"))
```

ASH results:

```{r sim 2}
load(paste0(outputdir, "mr.ash_20200429-2-mr.ash-res.Rd"))
summary_mr.ash(mr.ash.fit)
```

@@

True parameters:
```{r para 3}
readLines(paste0(outputdir, "param-20200429-3.R"))
```

ASH results:

```{r sim 3}
load(paste0(outputdir, "mr.ash_20200429-3-mr.ash-res.Rd"))
summary_mr.ash(mr.ash.fit)
```

@@

True parameters:
```{r para 4}
readLines(paste0(outputdir, "param-20200429-4.R"))
```

ASH results:

```{r sim 4}
load(paste0(outputdir, "mr.ash_20200429-4-mr.ash-res.Rd"))
summary_mr.ash(mr.ash.fit)
```

>>>>

plot_pip <- function(indi, pip) {
  barplot(indi)
}

@@

MR.ASH results (start from gene):
```{r sim 1 gene}
load(paste0(outputdir, "mr.ash2_20200503-1-mr.ash2.expr-res.Rd"))
g.fit <- mr.ash2.fit$fit1
s.fit <-  mr.ash2.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)
```

MR.ASH results (start from SNP):
```{r sim 1 snp}
load(paste0(outputdir, "mr.ash2_20200503-1-mr.ash2.snp-res.Rd"))
g.fit <- mr.ash2.fit$fit2
s.fit <-  mr.ash2.fit$fit1
summary_mr.ash2(g.fit, s.fit, phenores)
```

@@

True parameters:
```{r para 2}
load(paste0(outputdir, "mr.ash2_20200503-2-pheno.Rd"))
readLines(paste0(outputdir, "param-20200503-2.R"))
```

MR.ASH results (start from gene):
```{r sim 2 gene}
load(paste0(outputdir, "mr.ash2_20200503-2-mr.ash2.expr-res.Rd"))
g.fit <- mr.ash2.fit$fit1
s.fit <-  mr.ash2.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)
```

MR.ASH results (start from SNP):
```{r sim 2 snp}
load(paste0(outputdir, "mr.ash2_20200503-2-mr.ash2.snp-res.Rd"))
g.fit <- mr.ash2.fit$fit2
s.fit <-  mr.ash2.fit$fit1
summary_mr.ash2(g.fit, s.fit, phenores)
```

@@

True parameters:
```{r para 3}
load(paste0(outputdir, "mr.ash2_20200503-3-pheno.Rd"))
readLines(paste0(outputdir, "param-20200503-3.R"))
```

MR.ASH results (start from gene):
```{r sim 3 gene}
load(paste0(outputdir, "mr.ash2_20200503-3-mr.ash2.expr-res.Rd"))
g.fit <- mr.ash2.fit$fit1
s.fit <-  mr.ash2.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)
```

MR.ASH results (start from SNP):
```{r sim 3 snp}
load(paste0(outputdir, "mr.ash2_20200503-3-mr.ash2.snp-res.Rd"))
g.fit <- mr.ash2.fit$fit2
s.fit <-  mr.ash2.fit$fit1
summary_mr.ash2(g.fit, s.fit, phenores)
```

@@

True parameters:
```{r para 4}
load(paste0(outputdir, "mr.ash2_20200503-4-pheno.Rd"))
readLines(paste0(outputdir, "param-20200503-4.R"))
```

MR.ASH results (start from gene):
```{r sim 4 gene}
load(paste0(outputdir, "mr.ash2_20200503-4-mr.ash2.expr-res.Rd"))
g.fit <- mr.ash2.fit$fit1
s.fit <-  mr.ash2.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)
```

MR.ASH results (start from SNP):
```{r sim 4 snp}
load(paste0(outputdir, "mr.ash2_20200503-4-mr.ash2.snp-res.Rd"))
g.fit <- mr.ash2.fit$fit2
s.fit <-  mr.ash2.fit$fit1
summary_mr.ash2(g.fit, s.fit, phenores)
```
